### 2020-08-04 confirm-activity/tex/confirm-service-activity.tex
fix the discussion section

\subsection{PCD-based Scheme.}
The main idea here is to adapt the PCD framework so that Ursula
can combine the correctness proofs she computes for Bobs' requests in a single proof 
attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
requests correctly."

Thus, in this setup, there is only one computation party, or prover, namely, Ursula. 
For each round, where a round could be the time needed to mine a block on the 
blockchain, Ursula starts with input $x_1$, which is a signed and fresh request
from Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness 
proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, 
which is the input for the next step in the computation, Ursula answers 
this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then 
it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
$\hat{\pi}_2$ does not only 
attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served 
two valid distinct requests until now. The same process is repeated until the end of the 
round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of 
served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
this process pictorially.

@@

\subsection{CoSi-based Scheme.}
This solution utilizes the idea of collective signing by electing a committee 
that will sign a report submitted by a specific Ursula after verifying that 
the report supports the claim that ``Ursula has served $\omega$ distinct 
re-encryption requests correctly."

@@

\paragraph{On the committee election.} This can be done
by using some deterministic computation over a block hash and mapping
the output to Ursulas' public keys. So the selection is not determined by the
working Ursula to prevent any potential collusion. The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.

@@

\paragraph{On the publicity of the signed records.} Having a 
valid collective signature from a committee (that has at least one honest 
member) suffices for the correctness of the signed statement. However, 
it could be better to keep the records that produced the message $m$  
available for a while so that any party can verify them (the verifying
parties could maintain such a public record for a given period after which
the logs can be discarded).

@@

\paragraph{On compensating the committee.} This solution may 
raise the question of why would the elected committee (especially if it 
is composed of other Ursulas in the system) participate in the CoSi 
process, which also involves verifying the full request record presented 
by the working Ursula. This can be pictured as a collaborative
work, the committee does the work so that others will do the same
when the committee members play the role of working Ursulas.

@@

\subsection{Commit/Challenge/Open-based Scheme.}
This solution utilizes the idea of commit/challenge/open protocols. 
In details, Ursula keeps track of the requests coming from Bob(s) 
during a time round and assign each of them a unique sequence 
number. That is, Ursula replies with $cFrag$ and the correctness proof 
along with a sequence number showing the order of the request within 
the batch of requests handled during a round. At the end of the round, 
Ursula constructs a Merkle tree of all requests, where 
the requests (and their replies) are the leaves of the tree ordered by the sequence
numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
to the network (recall that $\omega$ is the number of served requests).

@@

An alternative approach to the challenge/open scheme described above is to 
have Ursula publish the full Merkle tree on some known public space but
not on the blockchain, and make the full record available online for a specific period
to allow anyone to verify the work. If no one files a complaint about the tree (we
still need to define correctness properties, like checking all Bob public keys are 
defined in the policy created by Alice, and that the response is valid by checking the 
proof produced by Umbral), Ursula collects the fees for the provided service. On the other
hand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.

>>>>

\subsection{ZKP-based Scheme}
The main idea here is to adapt the PCD framework so that Ursula can combine the correctness proofs she computes for Bobs' requests in a single proof attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption requests correctly."

Thus, in this setup, there is only one computation party, or prover, namely, Ursula. For each round, where a round could be the time needed to mine a block on the blockchain, Ursula starts with input $x_1$, which is a signed and fresh requestfrom Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, which is the input for the next step in the computation, Ursula answers this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. $\hat{\pi}_2$ does not only attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served two valid distinct requests until now. The same process is repeated until the end of the round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
this process pictorially.

@@

\subsection{CoSi-based Scheme}
This solution utilizes the idea of collective signing by electing a committee that will sign a report submitted by a specific Ursula after verifying that the report supports the claim that ``Ursula has served $\omega$ distinct re-encryption requests correctly."

@@

\paragraph{\bf On the committee election.} 
This can be done by using some deterministic computation over a block hash and mapping the output to Ursulas' public keys. So the selection is not determined by the working Ursula to prevent any potential collusion. The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.

@@

\paragraph{\bf On the publicity of the signed records.} 
Having a valid collective signature from a committee (that has at least one honest member) suffices for the correctness of the signed statement. However, it could be better to keep the records that produced the message $m$  available for a while so that any party can verify them (the verifying parties could maintain such a public record for a given period after which the logs can be discarded).

@@

\paragraph{\bf On compensating the committee.} 
This solution may raise the question of why would the elected committee (especially if it is composed of other Ursulas in the system) participate in the CoSi process, which also involves verifying the full request record presented by the working Ursula. This can be pictured as a collaborative work, the committee does the work so that others will do the same when the committee members play the role of working Ursulas.

@@

\subsection{Commit/Challenge/Open-based Scheme}
This solution utilizes the idea of commit/challenge/open protocols. In details, Ursula keeps track of the requests coming from Bob(s) during a time round and assign each of them a unique sequence number. That is, Ursula replies with $cFrag$ and the correctness proof along with a sequence number showing the order of the request within the batch of requests handled during a round. At the end of the round, Ursula constructs a Merkle tree of all requests, where the requests (and their replies) are the leaves of the tree ordered by the sequence numbers. Ursula signs the root of the tree, denoted as $root$ to produce a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ to the network (recall that $\omega$ is the number of served requests).

@@

An alternative approach to the challenge/open scheme described above is to have Ursula publish the full Merkle tree on some known public space but not on the blockchain, and make the full record available online for a specific period to allow anyone to verify the work. If no one files a complaint about the tree (we still need to define correctness properties, like checking all Bob public keys are defined in the policy created by Alice, and that the response is valid by checking the proof produced by Umbral), Ursula collects the fees for the provided service. On the otherhand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.

### 2020-08-04 confirm-activity/tex/discussion.tex
fix the discussion section

\section{Discussion and Analysis}
\label{discussion}
Which solution to adopt will be based on benchmark testing and the development vision of the NuCypher network. The ZKP-based solution (the one utilizing bulletproofs) provides several advantages including non-interactivity (as opposed to the committee-attestation one that needs interaction with the committee). It also supports computational soundness as opposed to the statistical one of the commit/challenge/open solution. Nonetheless, it could be the case that the other solutions are more efficient especially if we incorporate committee attestation or sidechains to support other functionalities in the network.

Another issue pertains to the payment computation. During early stages when the network launches, we anticipate  limited adoption and service demand. Thus, we reward Ursulas for just being online to encourage adoption. While in later stages, payments will be dispensed partially in proportion to the actual number of service requests an Ursula answers. This is due to the fact that later on the subsidies will effectively disappear, i.e., the majority of tokens in the network will be minted, and the service fees are the only source of income. To incentivize Ursula to provide a correct and timely service, these fees should be computed based on the actual amount of service. This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.

>>>>

\section{Discussion}
\label{discussion}
As we mentioned earlier, now in the NuCypher network, we have the naive confirm activity function calling approach, with a financial punishment of slashing the stake of any Ursula who does not log her activity periodically. Our early plans will be to replace this approach with the confirm availability solution introduced in Section~\ref{confirm-availability}.

For the confirm service activity, which will be deployed at a later of the network, which solution to adopt will be based on benchmark testing and the development vision of the NuCypher network. The ZKP-based solution (the one utilizing bulletproofs) provides several advantages including non-interactivity, as opposed to the committee-attestation one that needs interaction with the committee. It also supports computational soundness as opposed to the statistical one of the commit/challenge/open solution. Nonetheless, it could be the case that the committee-attestation and the Merkle-tree based solutions are more efficient especially if we incorporate committee attestation or sidechains to support other functionalities in the network.

Another related issue to confirm activity is the service payment strategy in the network. Until now we assume that Alice pays for the service by using the Ether she locks into the policy contract. Other arrangement may emerge in the system like having Bob pay for the requests he issues. Such an arrangement may have an implication on the confirm activity issue, and studying its impact, if it becomes part of the NuCypher network protocol, will be part pf our future work.
